Kindly Bent to Free Us

### 2020-02-28 kindly/intro.tex
region

\begin{figure}[tp]
  \begin{subfigure}[t]{0.53\linewidth}
    \lstinputlisting{code/writefiles.affe}
    \vspace{-15pt}
    \caption{File API}
    \label{fig:writing-files-api}
  \end{subfigure}~
  \begin{subfigure}[t]{0.43\linewidth}
\begin{lstlisting}
let main () =
  let h = File.fopen "foo" in
  File.write &!h "Hello ";
  File.write &!h "world!";
  File.close h
\end{lstlisting}
    \vspace{-10pt}
    \caption{File example}
    \label{fig:writing-files-example}
  \end{subfigure}
  \vspace{-10pt}
  \caption{Writing files}
  \label{fig:writing-files}
\end{figure}

@@

This example demonstrates three features of our system:
\begin{enumerate}
\item full type inference without annotations in user code (\cref{fig:writing-files-example}),
\item types carry multiplicity annotations in the form of kinds,
\item resource APIs can be written in direct style as linearity is a
  property of the type @File.t@.
\end{enumerate}

>>>>

\begin{figure}[tp]
  \begin{subfigure}[t]{0.53\linewidth}
    \lstinputlisting{code/writefiles.affe}
    \vspace{-15pt}
    \caption{File API}
    \label{fig:writing-files-api}
  \end{subfigure}~
  \begin{subfigure}[t]{0.43\linewidth}
\begin{lstlisting}
let main () =
  let h = File.fopen "foo" in
  File.write &!h "Hello ";(*@\label{line:hello}*)
  File.write &!h "world!";(*@\label{line:world}*)
  File.close h
\end{lstlisting}
    \vspace{-10pt}
    \caption{File example}
    \label{fig:writing-files-example}
  \end{subfigure}
  \vspace{-10pt}
  \caption{Writing files}
  \label{fig:writing-files}
\end{figure}

@@

Every borrow is restricted to a \emph{region}, i.e., a lexically
scoped program fragment from which the borrow must not escape. In
\cref{fig:writing-files-example}, there are two regions, one 
consisting of \cref{line:hello} and another consisting of
\cref{line:world}. Both are fully contained in the scope of the linear
handle @h@, hence we can take one exclusive borrow @&!h@ in each
region. In both regions the borrow is consumed immediately by passing
it to @File.write@. Regions are generally inferred by \lang.

This example demonstrates three features of our system:
\begin{enumerate}
\item type and region inference without annotations in user code (\cref{fig:writing-files-example}),
\item types carry multiplicity annotations in the form of kinds,
\item resource APIs can be written in direct style as linearity is a
  property of the type @File.t@.
\end{enumerate}
